---
title: "Shapley Decomposition: Other dimensions"
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'Shapley Decomposition Robustness.html'))})
---

#### Define Libraries
```{r echo=TRUE, message=FALSE, warning=FALSE, tidy=TRUE}

library("stringr")
library("dplyr")
library("ggplot2")
library("gridExtra")
library("knitr")
library("tidyverse")
library("magrittr")
library("foreign")
library("AER")
library("ggpubr")
library("devtools")
library("dineq")
library("reldist")
library("ineq")
library("patchwork")
library("hash")
```

#### Define Path
```{r tidy=TRUE}
dir.wrk <- getwd()
dir.data <- file.path(dir.wrk, "dataset/data")
dir.outdata <- file.path(dir.wrk, "dataset/outputdata")
dir.plot <- file.path(dir.wrk, "dataset/plots_decomp")
```

#### Define Files and load data
```{r tidy=TRUE}
file.dat <- file.path(dir.outdata, "dat_ineq.csv")
dat_p <- read.csv(file.dat, header=TRUE, stringsAsFactors=FALSE)
```

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

#### Decomposition by League of Conservation Voters (LCV) Scorecard
```{r}
## define by_year function
by_year <- function(dat_p, yr) {
  return(dat_p %>% filter(Year == yr))
}

## weighted
wtlcv <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- gini_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$HL_LCV, weights = ha[[i]]$pop_mi)
    hb[[i]] <- bar["gini_decomp"]
  }
  return(hb)
}
wt_lcv <- wtlcv(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_wtlcv <- as.list(wt_lcv)
wlcv <- lapply(list_wtlcv, function(x) x[1]$gini_decomp)
df_wtlcv <- do.call(rbind.data.frame, wlcv)
df_wtlcv <- cbind(Year=as.numeric(rownames(df_wtlcv)), df_wtlcv)
rownames(df_wtlcv) <- NULL
df_wtlcv <- df_wtlcv[order(df_wtlcv$Year, decreasing = FALSE),]
wtg_lcv <- df_wtlcv %>% rename(wtotal=gini_total, 
                                     wwithin=gini_within, wbetween=gini_between, woverlap=gini_overlap)

## unweighted
unlcv <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- gini_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$HL_LCV)
    hb[[i]] <- bar["gini_decomp"]
  }
  return(hb)
}
un_lcv <- unlcv(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_unlcv <- as.list(un_lcv)
unlcv <- lapply(list_unlcv, function(x) x[1]$gini_decomp)
df_unlcv <- do.call(rbind.data.frame, unlcv)
df_unlcv <- cbind(Year=as.numeric(rownames(df_unlcv)), df_unlcv)
rownames(df_unlcv) <- NULL
df_unlcv <- df_unlcv[order(df_unlcv$Year, decreasing = FALSE),]
un_lcv <- df_unlcv %>% rename(total=gini_total, 
                                     within=gini_within, between=gini_between, overlap=gini_overlap)
decomp_lcv <-left_join(un_lcv, wtg_lcv)

```

#### Plot data preparation LCV
```{r}
dlcv <- reshape2::melt(decomp_lcv, id.vars="Year")
dlcv$Group <- ifelse((dlcv$variable == "wtotal") | (dlcv$variable == "total"), "Overall",
                       ifelse((dlcv$variable == "wwithin") | (dlcv$variable == "within"), "Within group",
                              ifelse((dlcv$variable == "wbetween") | (dlcv$variable == "between"),"Between group","Overlap")))


dlcv$Weight <- ifelse((dlcv$variable == "wtotal") | (dlcv$variable == "wwithin") | 
                          (dlcv$variable == "wbetween") | (dlcv$variable == "woverlap"), "Population weighted", "Unweighted")

dlcv$Group <- factor(dlcv$Group, levels=c("Overall","Within group", "Between group", "Overlap"))
dlcv$Weight <- factor(dlcv$Weight, levels=c("Population weighted","Unweighted"))
```

#### Plot: decompotions by LCV
```{r fig.height = 3, fig.width = 3, fig.align = "center"}
plcv<-ggplot(dlcv, aes(x=Year))+
  geom_line(aes(y = value, color = Group, linetype = Weight), size=0.7) +
  scale_colour_manual(values=c("black", "green","blue", "red")) + 
  scale_linetype_manual(values=c("solid","dotted")) +
  labs(x = "High and low LCV score states", y = "")+
  theme(text=element_text(size=8))+
  scale_x_continuous(breaks=c(1997, 2000, 2003, 2006, 2009, 2012, 2015, 2019, 2021)) +
  scale_y_continuous(limits = c(0, 0.36), breaks = seq(0, 0.36, 0.04)) +
  theme(axis.text.x = element_text(angle = 45, vjust=0.5))+
  theme(axis.title.x = element_text(size = 8))+
  theme(legend.title = element_blank())+
  theme(legend.direction = "horizontal") +
  theme(legend.position = "none", legend.margin = margin(t = -7)) +
  theme(legend.box = "vertical")+
  theme(legend.background = element_rect(fill = "transparent")) +
  theme(legend.spacing.x = unit(0.2, "lines"))+
  theme(legend.spacing.y = unit(0.6, "lines"))+
  theme(legend.key.width = unit(0.4, 'cm'))+
  theme(legend.key.height = unit(0.4, 'cm'))+
  theme(legend.text = element_text(size=6))
```

#### Decomposition by Energy Expenditure 
```{r}
## weighted
wtexpend <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- gini_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$HL_Expend, weights = ha[[i]]$pop_mi)
    hb[[i]] <- bar["gini_decomp"]
  }
  return(hb)
}
wt_expend <- wtexpend(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_wtexp <- as.list(wt_expend)
wexp <- lapply(list_wtexp, function(x) x[1]$gini_decomp)
df_wtexp <- do.call(rbind.data.frame, wexp)
df_wtexp <- cbind(Year=as.numeric(rownames(df_wtexp)), df_wtexp)
rownames(df_wtexp) <- NULL
df_wtexp <- df_wtexp[order(df_wtexp$Year, decreasing = FALSE),]
wtg_exp <- df_wtexp %>% rename(wtotal=gini_total, 
                                     wwithin=gini_within, wbetween=gini_between, woverlap=gini_overlap)

## unweighted
unexp <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- gini_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$HL_Expend)
    hb[[i]] <- bar["gini_decomp"]
  }
  return(hb)
}
un_exp <- unexp(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_unexp <- as.list(un_exp)
unexp <- lapply(list_unexp, function(x) x[1]$gini_decomp)
df_unexp <- do.call(rbind.data.frame, unexp)
df_unexp <- cbind(Year=as.numeric(rownames(df_unexp)), df_unexp)
rownames(df_unexp) <- NULL
df_unexp <- df_unexp[order(df_unexp$Year, decreasing = FALSE),]
un_exp <- df_unexp %>% rename(total=gini_total, 
                                     within=gini_within, between=gini_between, overlap=gini_overlap)
decomp_exp <-left_join(un_exp, wtg_exp)

```

#### Plot data preparation: Energy Expenditure 
```{r}
dexp <- reshape2::melt(decomp_exp, id.vars="Year")
dexp$Group <- ifelse((dexp$variable == "wtotal") | (dexp$variable == "total"), "Overall",
                       ifelse((dexp$variable == "wwithin") | (dexp$variable == "within"), "Within group",
                              ifelse((dexp$variable == "wbetween") | (dexp$variable == "between"),"Between group","Overlap")))


dexp$Weight <- ifelse((dexp$variable == "wtotal") | (dexp$variable == "wwithin") | 
                          (dexp$variable == "wbetween") | (dexp$variable == "woverlap"), "Population weighted", "Unweighted")

dexp$Group <- factor(dexp$Group, levels=c("Overall","Within group", "Between group", "Overlap"))
dexp$Weight <- factor(dexp$Weight, levels=c("Population weighted","Unweighted"))
```

#### Plot: decompotion by Energy Expenditure
```{r fig.height = 3, fig.width = 3, fig.align = "center"}
pexpend<-ggplot(dexp, aes(x=Year))+
  geom_line(aes(y = value, color = Group, linetype = Weight), size=0.7) +
  scale_colour_manual(values=c("black", "green","blue", "red")) + 
  scale_linetype_manual(values=c("solid","dotted")) +
  labs(x = "High and low energy expenditure states", y = "")+
  theme(text=element_text(size=8))+
  scale_x_continuous(breaks=c(1997, 2000, 2003, 2006, 2009, 2012, 2015, 2019, 2021)) +
  scale_y_continuous(limits = c(0, 0.36), breaks = seq(0, 0.36, 0.04)) +
  theme(axis.text.x = element_text(angle = 45, vjust=0.5))+
  theme(axis.title.x = element_text(size = 8))+
  theme(legend.title = element_blank())+
  theme(legend.direction = "horizontal") +
  theme(legend.position = "none", legend.margin = margin(t = -7)) +
  theme(legend.box = "vertical")+
  theme(legend.background = element_rect(fill = "transparent")) +
  theme(legend.spacing.x = unit(0.2, "lines"))+
  theme(legend.spacing.y = unit(0.6, "lines"))+
  theme(legend.key.width = unit(0.4, 'cm'))+
  theme(legend.key.height = unit(0.4, 'cm'))+
  theme(legend.text = element_text(size=6))
```

#### CO2 Gini decomposition by INCOME class (Rich versus Poor)
```{r}
#### Unweighted
foo_rp <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- gini_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$in_class)
    hb[[i]] <- bar["gini_decomp"]
  }
  return(hb)
}
gini_rp <- foo_rp(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
rp_decomp <- as.list(gini_rp)
rp <- lapply(rp_decomp, function(x) x[1]$gini_decomp)
rp_decomp <- do.call(rbind.data.frame, rp)
rp_decomp <- cbind(Year=as.numeric(rownames(rp_decomp)), rp_decomp)
rownames(rp_decomp) <- NULL
rp_decomp <- rp_decomp[order(rp_decomp$Year, decreasing = FALSE),]
rp_decomp <- rp_decomp %>% rename(total=gini_total, 
                                  within=gini_within, between=gini_between, overlap=gini_overlap)

## Population-weighted
wtfoo_rp <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- gini_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$in_class, weights = ha[[i]]$pop_mi)
    hb[[i]] <- bar["gini_decomp"]
  }
  return(hb)
}
wtgini_rp <- wtfoo_rp(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
rp_wtdecomp <- as.list(wtgini_rp)
wtrp <- lapply(rp_wtdecomp, function(x) x[1]$gini_decomp)
rp_wtdecomp <- do.call(rbind.data.frame, wtrp)
rp_wtdecomp <- cbind(Year=as.numeric(rownames(rp_wtdecomp)), rp_wtdecomp)
rownames(rp_wtdecomp) <- NULL
rp_wtdecomp <- rp_wtdecomp[order(rp_wtdecomp$Year, decreasing = FALSE),]
rp_wtdecomp <- rp_wtdecomp %>% rename(wtotal=gini_total, 
                                      wwithin=gini_within, wbetween=gini_between, woverlap=gini_overlap)
```

#### Join weighted and unweighted data files: decomposition by income class
```{r}
decomp_income <-left_join(rp_wtdecomp, rp_decomp)
```
</br>

#### Plot data preparation: income class 
```{r}
dincome <- reshape2::melt(decomp_income, id.vars="Year")
dincome$Group <- ifelse((dincome$variable == "wtotal") | (dincome$variable == "total"), "Overall",
                       ifelse((dincome$variable == "wwithin") | (dincome$variable == "within"), "Within states",
                              ifelse((dincome$variable == "wbetween") | (dincome$variable == "between"),"Between rich & poor states","Overlap")))


dincome$Weight <- ifelse((dincome$variable == "wtotal") | (dincome$variable == "wwithin") | 
                          (dincome$variable == "wbetween") | (dincome$variable == "woverlap"), "Population weighted", "Unweighted")

dincome$Group <- factor(dincome$Group, levels=c("Overall","Within states", "Between rich & poor states", "Overlap"))
dincome$Weight <- factor(dincome$Weight, levels=c("Population weighted","Unweighted"))
```

#### Plot: decomposition by INCOME class
```{r fig.height = 3, fig.width = 3, fig.align = "center"}
pincome<-ggplot(dincome, aes(x=Year))+
  geom_line(aes(y = value, color = Group, linetype = Weight), size=0.7) +
  scale_colour_manual(values=c("black", "green","blue", "red")) +  
  scale_linetype_manual(values=c("solid","dotted")) +
  labs(x = "Rich and poor states", y = "")+
  theme(text=element_text(size=8))+
  scale_x_continuous(breaks=c(1997, 2000, 2003, 2006, 2009, 2012, 2015, 2019, 2021)) +
  #scale_x_continuous(breaks = seq(min(dincome$Year), max(dincome$Year), 1)) +
  scale_y_continuous(limits = c(0, 0.36), breaks = seq(0, 0.36, 0.04)) +
  theme(axis.text.x = element_text(angle = 45, vjust=0.5))+
  theme(axis.title.x = element_text(size = 8))+
  theme(legend.title = element_blank())+
  theme(legend.direction = "horizontal") +
  theme(legend.position = "none", legend.margin = margin(t = -7)) +
  theme(legend.box = "vertical")+
  theme(legend.background = element_rect(fill = "transparent")) +
  theme(legend.spacing.x = unit(0.2, "lines"))+
  theme(legend.spacing.y = unit(0.6, "lines"))+
  theme(legend.key.width = unit(0.4, 'cm'))+
  theme(legend.key.height = unit(0.4, 'cm'))+
  theme(legend.text = element_text(size=6))
```

#### Join plots: Decomposition by LCV, Energy Expenditure and Income
```{r fig.height = 3.5, fig.width = 7, fig.align = "center"}

decomp_lcv_exp_in <-ggarrange(pexpend, plcv, pincome, labels = c("a", "b", "c"), hjust = -2.0, 
                                font.label = list(size = 8, color = "black", face = "bold"), 
                                ncol = 3, nrow = 1, legend="none")
decomp_lcv_exp_in
```

#### Decomposition by Geography
```{r}
## weighted
wtgeo <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- gini_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$Geography, weights = ha[[i]]$pop_mi)
    hb[[i]] <- bar["gini_decomp"]
  }
  return(hb)
}
wtgeod <- wtgeo(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_wtgeo <- as.list(wtgeod)
wgeo <- lapply(list_wtgeo, function(x) x[1]$gini_decomp)
df_wtgeo <- do.call(rbind.data.frame, wgeo)
df_wtgeo <- cbind(Year=as.numeric(rownames(df_wtgeo)), df_wtgeo)
rownames(df_wtgeo) <- NULL
df_wtgeo <- df_wtgeo[order(df_wtgeo$Year, decreasing = FALSE),]
wtg_geo <- df_wtgeo %>% rename(wtotal=gini_total, 
                                     wwithin=gini_within, wbetween=gini_between, woverlap=gini_overlap)

## unweighted
ungeo <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- gini_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$Geography)
    hb[[i]] <- bar["gini_decomp"]
  }
  return(hb)
}
ungeod <- ungeo(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_ungeo <- as.list(ungeod)
ug <- lapply(list_ungeo, function(x) x[1]$gini_decomp)
df_ungeo <- do.call(rbind.data.frame, ug)
df_ungeo <- cbind(Year=as.numeric(rownames(df_ungeo)), df_ungeo)
rownames(df_ungeo) <- NULL
df_ungeo <- df_ungeo[order(df_ungeo$Year, decreasing = FALSE),]
ug_geo <- df_ungeo %>% rename(total=gini_total, 
                                 within=gini_within, between=gini_between, overlap=gini_overlap)

## Join two data files
decomp_geo <-left_join(ug_geo, wtg_geo)
```

#### Data preparation: Geography
```{r fig.height = 5, fig.width = 7, fig.align = "center"}

dgeo <- reshape2::melt(decomp_geo, id.vars="Year")
dgeo$Group <- ifelse((dgeo$variable == "wtotal") | (dgeo$variable == "total"), "Overall",
                       ifelse((dgeo$variable == "wwithin") | (dgeo$variable == "within"), "Within group",
                              ifelse((dgeo$variable == "wbetween") | (dgeo$variable == "between"),"Between group","Overlap")))


dgeo$Weight <- ifelse((dgeo$variable == "wtotal") | (dgeo$variable == "wwithin") | 
                          (dgeo$variable == "wbetween") | (dgeo$variable == "woverlap"), "Population Weighted", "Unweighted")

dgeo$Group <- factor(dgeo$Group, levels=c("Overall","Within group", "Between group", "Overlap"))
dgeo$Weight <- factor(dgeo$Weight, levels=c("Population Weighted","Unweighted"))
```
</br>

#### Decompostion plot: Geography
```{r fig.height = 3, fig.width = 4, fig.align = "center"}
pgeo<-ggplot(dgeo, aes(x=Year))+
  geom_line(aes(y = value, color = Group, linetype = Weight), size=0.7) +
  scale_linetype_manual(values=c("solid","dotted")) +
  labs(x = "Coastal and non-coastal states", y = "")+
  theme(text=element_text(size=8))+
  scale_y_continuous(limits = c(0, 0.36), breaks = seq(0, 0.36, 0.04)) +
  scale_x_continuous(breaks=c(1997, 2000, 2003, 2006, 2009, 2012, 2015, 2019, 2021)) +
  theme(axis.text.x = element_text(angle = 45, vjust=0.5))+
  theme(legend.title = element_blank())+
  theme(legend.direction = "horizontal") +
  theme(legend.position = "bottom", legend.margin=margin(t= 1), legend.justification="center") +
  theme(legend.box = "vertical")+
  theme(legend.background = element_rect(fill = "transparent")) +
  theme(legend.spacing.x = unit(0.2, "lines"))+
  theme(legend.spacing.y = unit(0.6, "lines"))+
  guides(linetype = guide_legend(order = 1),col = guide_legend(order = 2))+
  theme(legend.key.width = unit(0.35, 'cm'))+
  theme(legend.key.height = unit(0.4, 'cm'))+
  theme(legend.text = element_text(size=6))+
  scale_color_manual(labels = c("Overall", "Within group", "Between group", "Overlap"), values=c("black", "green","blue", "red"))
```

#### Decomposition by Heating Degree Days
```{r}
## Weighted
wthdd <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- gini_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$HDD, weights = ha[[i]]$pop_mi)
    hb[[i]] <- bar["gini_decomp"]
  }
  return(hb)
}
wth_days <- wthdd(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_wtheat <- as.list(wth_days)
wheat <- lapply(list_wtheat, function(x) x[1]$gini_decomp)
df_wtheat <- do.call(rbind.data.frame, wheat)
df_wtheat <- cbind(Year=as.numeric(rownames(df_wtheat)), df_wtheat)
rownames(df_wtheat) <- NULL
df_wtheat <- df_wtheat[order(df_wtheat$Year, decreasing = FALSE),]
wtg_heat <- df_wtheat %>% rename(wtotal=gini_total, 
                                     wwithin=gini_within, wbetween=gini_between, woverlap=gini_overlap)

## unweighted
unheat <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- gini_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$HDD)
    hb[[i]] <- bar["gini_decomp"]
  }
  return(hb)
}
unh_days <- unheat(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_unheat <- as.list(unh_days)
unheat <- lapply(list_unheat, function(x) x[1]$gini_decomp)
df_unheat <- do.call(rbind.data.frame, unheat)
df_unheat <- cbind(Year=as.numeric(rownames(df_unheat)), df_unheat)
rownames(df_unheat) <- NULL
df_unheat <- df_unheat[order(df_unheat$Year, decreasing = FALSE),]
un_heat <- df_unheat %>% rename(untotal=gini_total, 
                                     unwithin=gini_within, unbetween=gini_between, unoverlap=gini_overlap)

## join two data files
decomp_hdd <-left_join(un_heat, wtg_heat)
```

#### Data preparation: HDD
```{r}

dheat <- reshape2::melt(decomp_hdd, id.vars="Year")
dheat$Group <- ifelse((dheat$variable == "wtotal") | (dheat$variable == "untotal"), "Overall",
                       ifelse((dheat$variable == "wwithin") | (dheat$variable == "unwithin"), "Within group",
                              ifelse((dheat$variable == "wbetween") | (dheat$variable == "unbetween"),"Between group","Overlap")))


dheat$Weight <- ifelse((dheat$variable == "wtotal") | (dheat$variable == "wwithin") | 
                          (dheat$variable == "wbetween") | (dheat$variable == "woverlap"), "Population Weighted", "Unweighted")

dheat$Group <- factor(dheat$Group, levels=c("Overall","Within group", "Between group", "Overlap"))
dheat$Weight <- factor(dheat$Weight, levels=c("Population Weighted","Unweighted"))
```

#### Decompostion plot: HDD
```{r fig.height = 3, fig.width = 4, fig.align = "center"}

pheat<-ggplot(dheat, aes(x=Year))+
  geom_line(aes(y = value, color = Group, linetype = Weight), size=0.7) +
  scale_linetype_manual(values=c("solid","dotted")) +
  labs(x = "High and low heating degree days", y = "")+
  theme(text=element_text(size=8))+
  scale_y_continuous(limits = c(0, 0.36), breaks = seq(0, 0.36, 0.04)) +
  scale_x_continuous(breaks=c(1997, 2000, 2003, 2006, 2009, 2012, 2015, 2019, 2021)) +
  theme(axis.text.x = element_text(angle = 45, vjust=0.5))+
  theme(legend.title = element_blank())+
  theme(legend.direction = "horizontal") +
  theme(legend.position = "bottom", legend.margin=margin(t= 1)) +
  theme(legend.box = "vertical")+
  theme(legend.background = element_rect(fill = "transparent")) +
  theme(legend.spacing.x = unit(0.3, "lines"))+
  theme(legend.spacing.y = unit(0.6, "lines"))+
  theme(legend.key.width = unit(0.35, 'cm'))+
  theme(legend.key.height = unit(0.4, 'cm'))+
  theme(legend.text = element_text(size=7))+
  scale_color_manual(labels = c("Overall", "Within group", "Between group", "Overlap"), values=c("black", "green","blue", "red"))
```

#### Decomposition by Cooling Degree Days
```{r}
## weighted
wtcdd <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- gini_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$CDD, weights = ha[[i]]$pop_mi)
    hb[[i]] <- bar["gini_decomp"]
  }
  return(hb)
}
wtc_days <- wtcdd(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_wtcool <- as.list(wtc_days)
wcool <- lapply(list_wtcool, function(x) x[1]$gini_decomp)
df_wtcool <- do.call(rbind.data.frame, wcool)
df_wtcool <- cbind(Year=as.numeric(rownames(df_wtcool)), df_wtcool)
rownames(df_wtcool) <- NULL
df_wtcool <- df_wtcool[order(df_wtcool$Year, decreasing = FALSE),]
wtg_cool <- df_wtcool %>% rename(wtotal=gini_total, 
                                     wwithin=gini_within, wbetween=gini_between, woverlap=gini_overlap)

## unweighted
uncool <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- gini_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$CDD)
    hb[[i]] <- bar["gini_decomp"]
  }
  return(hb)
}
unc_days <- uncool(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_uncool <- as.list(unc_days)
uncool <- lapply(list_uncool, function(x) x[1]$gini_decomp)
df_uncool <- do.call(rbind.data.frame, uncool)
df_uncool <- cbind(Year=as.numeric(rownames(df_uncool)), df_uncool)
rownames(df_uncool) <- NULL
df_uncool <- df_uncool[order(df_uncool$Year, decreasing = FALSE),]
un_cool <- df_uncool %>% rename(untotal=gini_total, 
                                     unwithin=gini_within, unbetween=gini_between, unoverlap=gini_overlap)

## join two data files
decomp_cdd <-left_join(un_cool, wtg_cool)
```

#### Data preparation: CDD
```{r}

dcool <- reshape2::melt(decomp_cdd, id.vars="Year")
dcool$Group <- ifelse((dcool$variable == "wtotal") | (dcool$variable == "untotal"), "Overall",
                       ifelse((dcool$variable == "wwithin") | (dcool$variable == "unwithin"), "Within group",
                              ifelse((dcool$variable == "wbetween") | (dcool$variable == "unbetween"),"Between group","Overlap")))


dcool$Weight <- ifelse((dcool$variable == "wtotal") | (dcool$variable == "wwithin") | 
                          (dcool$variable == "wbetween") | (dcool$variable == "woverlap"), "Population Weighted", "Unweighted")

dcool$Group <- factor(dcool$Group, levels=c("Overall","Within group", "Between group", "Overlap"))
dheat$Weight <- factor(dheat$Weight, levels=c("Population Weighted","Unweighted"))
```

#### Decompostion plot: CDD
```{r fig.height = 3, fig.width = 4, fig.align = "center"}

pcool<-ggplot(dcool, aes(x=Year))+
  geom_line(aes(y = value, color = Group, linetype = Weight), size=0.7) +
  scale_linetype_manual(values=c("solid","dotted")) +
  labs(x = "High and low cooling degree days", y = "")+
  theme(text=element_text(size=8))+
  scale_y_continuous(limits = c(0, 0.36), breaks = seq(0, 0.36, 0.04)) +
  scale_x_continuous(breaks=c(1997, 2000, 2003, 2006, 2009, 2012, 2015, 2019, 2021)) +
  theme(axis.text.x = element_text(angle = 45, vjust=0.5))+
  theme(legend.title = element_blank())+
  theme(legend.direction = "horizontal") +
  theme(legend.position = "bottom", legend.margin=margin(t= 1)) +
  theme(legend.box = "vertical")+
  theme(legend.background = element_rect(fill = "transparent")) +
  theme(legend.spacing.x = unit(0.3, "lines"))+
  theme(legend.spacing.y = unit(0.6, "lines"))+
  guides(linetype = guide_legend(order = 1),col = guide_legend(order = 2))+
  theme(legend.key.width = unit(0.35, 'cm'))+
  theme(legend.key.height = unit(0.4, 'cm'))+
  theme(legend.text = element_text(size=7))+
  scale_color_manual(labels = c("Overall", "Within group", "Between group", "Overlap"), values=c("black", "green","blue", "red"))
```

#### Decomposition Plot by Geography and Heating/Cooling Degree Days
```{r fig.height = 3.5, fig.width = 7, fig.align = "center"}

decomp_geo_ddays <-ggarrange(pgeo, pheat, pcool, labels = c("d", "e", "f"), hjust = -2.0, 
                                font.label = list(size = 8, color = "black", face = "bold"), 
                                ncol = 3, nrow = 1, common.legend = TRUE, legend ="bottom")
decomp_geo_ddays
```

#### Decomposition Plots Together
```{r fig.height = 5, fig.width = 7, fig.align = "center"}
decomp_robust <- cowplot::plot_grid(decomp_lcv_exp_in, decomp_geo_ddays, nrow=2, rel_heights = c(1, 1.15))
robust_decompostion <- annotate_figure(decomp_robust, left = text_grob("Decomposition of per capita CO2 Gini", rot=90, size=8))

robust_decompostion

## final plot output
file.plot <- file.path(dir.plot, "robust_decomp.png")
png(file.plot, height=5, width=7, units="in", bg= "white", res=300)
robust_decompostion
dev.off()
```

