---
title: "Shapley Decomposition MLD"
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'Shapley MLD.html'))})
---

#### Define Libraries
```{r echo=TRUE, message=FALSE, warning=FALSE, tidy=TRUE}

library("stringr")
library("dplyr")
library("ggplot2")
library("gridExtra")
library("knitr")
library("tidyverse")
library("magrittr")
library("foreign")
library("AER")
library("ggpubr")
library("devtools")
library("dineq")
library("reldist")
library("ineq")
library("patchwork")
library("hash")
```

#### Define Path
```{r tidy=TRUE}
dir.wrk <- getwd()
dir.data <- file.path(dir.wrk, "dataset/data")
dir.outdata <- file.path(dir.wrk, "dataset/outputdata")
dir.plot <- file.path(dir.wrk, "dataset/plots_decomp")
```

#### Define Files and load data
```{r tidy=TRUE}
file.dat <- file.path(dir.outdata, "dat_ineq.csv")
dat_p <- read.csv(file.dat, header=TRUE, stringsAsFactors=FALSE)
```

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

#### Mean Log Deviation
#### Decomposition of CO2 MLD by Party and Year
```{r}
## define by_year function
by_year <- function(dat_p, yr) {
  return(dat_p %>% filter(Year == yr))
}

## weighted
pmld_co <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- mld_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$Party, weights = ha[[i]]$pop_mi )
    hb[[i]] <- bar["mld_decomp"]
  }
  return(hb)
}
pmld_decomp <- pmld_co(dat_p)

### Parse Hash fuction
pmldco_decomp <- as.list(pmld_decomp)
pml <- lapply(pmldco_decomp, function(x) x[1]$mld_decomp)
pmldco_decomp <- do.call(rbind.data.frame, pml)
pmldco_decomp <- cbind(Year=as.numeric(rownames(pmldco_decomp)), pmldco_decomp)
rownames(pmldco_decomp) <- NULL
pmldco_d <- pmldco_decomp[order(pmldco_decomp$Year, decreasing = FALSE),]
pmldco_d <- pmldco_d %>% rename(pmld=mld_total, pwithin=mld_within, pbetween=mld_between)

## unweighted
pumld_co <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- mld_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$Party)
    hb[[i]] <- bar["mld_decomp"]
  }
  return(hb)
}
pumld_decomp <- pumld_co(dat_p)

### Parse Hash fuction
pumldco_decomp <- as.list(pumld_decomp)
puml <- lapply(pumldco_decomp, function(x) x[1]$mld_decomp)
pumldco_decomp <- do.call(rbind.data.frame, puml)
pumld_d <- cbind(Year=as.numeric(rownames(pumldco_decomp)), pumldco_decomp)
rownames(pumld_d) <- NULL
pumldco_d <- pumld_d[order(pumld_d$Year, decreasing = FALSE),]
pumldco_d <- pumldco_d %>% rename(pumld=mld_total, puwithin=mld_within, pubetween=mld_between)
```
</br>

#### Decomposition of MLD by Party/Year: data preparation for a plot
```{r fig.height = 2, fig.width = 3, fig.align = "center"}
## Join files
decomp_pmld <-left_join(pmldco_d, pumldco_d)

## data preparation
dmld <- reshape2::melt(decomp_pmld, id.vars="Year")

dmld$Group <- ifelse((dmld$variable == "pmld") | (dmld$variable == "pumld"), "Overall",
                     ifelse((dmld$variable == "pwithin") | (dmld$variable == "puwithin"), "Within group", "Between group"))


dmld$Weight <- ifelse((dmld$variable == "pmld") | (dmld$variable == "pwithin") | 
                          (dmld$variable == "pbetween"), "Population weighted", "Unweighted")

dmld$Group <- factor(dmld$Group, levels=c("Overall","Within group", "Between group"))
dmld$Weight <- factor(dmld$Weight, levels=c("Population weighted","Unweighted"))

## Plot
pmld <-ggplot(dmld, aes(x=Year))+
  geom_line(aes(y = value, color = Group, linetype = Weight), size=0.7) +
  scale_colour_manual(values=c("black", "green","blue")) +  
  scale_linetype_manual(values=c("solid","dotted")) +
  labs(x = "Red and blue states", y = "")+
  theme(text=element_text(size=8))+
  #scale_x_continuous(breaks = seq(min(dparty$Year), max(dparty$Year), 1)) +
  scale_x_continuous(breaks=c(1997, 2000, 2003, 2006, 2009, 2012, 2015, 2019, 2021)) +
  scale_y_continuous(limits = c(0, 0.22), breaks = seq(0, 0.22, 0.02)) +
  theme(axis.text.x = element_text(angle = 45, vjust=0.5))+
  theme(legend.title = element_blank())+
  theme(legend.direction = "horizontal") +
  theme(legend.position = "none", legend.margin = margin(t = -5)) +
  theme(legend.box = "vertical")+
  theme(legend.background = element_rect(fill = "transparent")) +
  theme(legend.spacing.x = unit(0.3, "lines"))+
  theme(legend.spacing.y = unit(0.6, "lines"))+
  theme(legend.key.width = unit(0.6, 'cm'))+
  theme(legend.key.height = unit(0.5, 'cm'))+
  theme(legend.text = element_text(size=6))
```

#### Decomposition of MLD by LCV
```{r}
## Weighted
lmld_co <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- mld_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$HL_LCV, weights = ha[[i]]$pop_mi )
    hb[[i]] <- bar["mld_decomp"]
  }
  return(hb)
}
lmld_decomp <- lmld_co(dat_p)

### Parse Hash fuction
lmldco_decomp <- as.list(lmld_decomp)
lml <- lapply(lmldco_decomp, function(x) x[1]$mld_decomp)
lmldco_decomp <- do.call(rbind.data.frame, lml)
lmldco_decomp <- cbind(Year=as.numeric(rownames(lmldco_decomp)), lmldco_decomp)
rownames(lmldco_decomp) <- NULL
lmldco_d <- lmldco_decomp[order(lmldco_decomp$Year, decreasing = FALSE),]
lmldco_d <- lmldco_d %>% rename(lmld=mld_total, lwithin=mld_within, lbetween=mld_between)

## Unweighted
lumld_co <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- mld_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$HL_LCV)
    hb[[i]] <- bar["mld_decomp"]
  }
  return(hb)
}
lumld_decomp <- lumld_co(dat_p)

### Parse Hash fuction
lumldco_decomp <- as.list(lumld_decomp)
luml <- lapply(lumldco_decomp, function(x) x[1]$mld_decomp)
lumldco_decomp <- do.call(rbind.data.frame, luml)
lumld_d <- cbind(Year=as.numeric(rownames(lumldco_decomp)), lumldco_decomp)
rownames(lumld_d) <- NULL
lumldco_d <- lumld_d[order(lumld_d$Year, decreasing = FALSE),]
lumldco_d <- lumldco_d %>% rename(lumld=mld_total, luwithin=mld_within, lubetween=mld_between)
```
</br>

#### Decomposition of MLD by LCV
```{r fig.height = 2, fig.width = 3, fig.align = "center"}
## Join files
decomp_lmld <-left_join(lmldco_d, lumldco_d)

## Data preparation
lmld <- reshape2::melt(decomp_lmld, id.vars="Year")

lmld$Group <- ifelse((lmld$variable == "lmld") | (lmld$variable == "lumld"), "Overall",
                     ifelse((lmld$variable == "lwithin") | (lmld$variable == "luwithin"), "Within group", "Between group"))


lmld$Weight <- ifelse((lmld$variable == "lmld") | (lmld$variable == "lwithin") | 
                          (lmld$variable == "lbetween"), "Population weighted", "Unweighted")

lmld$Group <- factor(lmld$Group, levels=c("Overall","Within group", "Between group"))
lmld$Weight <- factor(lmld$Weight, levels=c("Population weighted","Unweighted"))
```

#### Plot by LCV
```{r fig.height = 3, fig.width = 7, fig.align = "center"}

lmld <-ggplot(lmld, aes(x=Year))+
  geom_line(aes(y = value, color = Group, linetype = Weight), size=0.7) +
  scale_colour_manual(values=c("black", "green","blue")) +  
  scale_linetype_manual(values=c("solid","dotted")) +
  labs(x = "High-low LCV score", y = "")+
  theme(text=element_text(size=8))+
  scale_x_continuous(breaks=c(1997, 2000, 2003, 2006, 2009, 2012, 2015, 2019, 2021)) +
  scale_y_continuous(limits = c(0, 0.22), breaks = seq(0, 0.22, 0.02)) +
  theme(axis.text.x = element_text(angle = 45, vjust=0.5))+
  theme(axis.text.y = element_blank())+
  theme(legend.title = element_blank())+
  theme(legend.direction = "horizontal") +
  theme(legend.position = "none", legend.margin = margin(t = -5)) +
  theme(legend.box = "vertical")+
  theme(legend.background = element_rect(fill = "transparent")) +
  theme(legend.spacing.x = unit(0.3, "lines"))+
  theme(legend.spacing.y = unit(0.6, "lines"))+
  theme(legend.key.width = unit(0.6, 'cm'))+
  theme(legend.key.height = unit(0.5, 'cm'))+
  theme(legend.text = element_text(size=6))
```

#### Decomposition of MLD by Energy Expenditure
```{r}
## Weighted
emld_co <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- mld_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$HL_Expend, weights = ha[[i]]$pop_mi )
    hb[[i]] <- bar["mld_decomp"]
  }
  return(hb)
}
emld_decomp <- emld_co(dat_p)

### Parse Hash fuction
emldco_decomp <- as.list(emld_decomp)
eml <- lapply(emldco_decomp, function(x) x[1]$mld_decomp)
emldco_decomp <- do.call(rbind.data.frame, eml)
emldco_decomp <- cbind(Year=as.numeric(rownames(emldco_decomp)), emldco_decomp)
rownames(emldco_decomp) <- NULL
emldco_d <- emldco_decomp[order(emldco_decomp$Year, decreasing = FALSE),]
emldco_d <- emldco_d %>% rename(emld=mld_total, ewithin=mld_within, ebetween=mld_between)

## Unweighted
eumld_co <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- mld_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$HL_Expend)
    hb[[i]] <- bar["mld_decomp"]
  }
  return(hb)
}
eumld_decomp <- eumld_co(dat_p)

### Parse Hash fuction
eumldco_decomp <- as.list(eumld_decomp)
euml <- lapply(eumldco_decomp, function(x) x[1]$mld_decomp)
eumldco_decomp <- do.call(rbind.data.frame, euml)
eumld_d <- cbind(Year=as.numeric(rownames(eumldco_decomp)), eumldco_decomp)
rownames(eumld_d) <- NULL
eumldco_d <- eumld_d[order(eumld_d$Year, decreasing = FALSE),]
eumldco_d <- eumldco_d %>% rename(eumld=mld_total, euwithin=mld_within, eubetween=mld_between)
```
</br>

#### Decomposition of MLD by Expenditure
```{r fig.height = 2, fig.width = 3, fig.align = "center"}
## Join files
decomp_emld <-left_join(emldco_d, eumldco_d)

## Data preparation
emld <- reshape2::melt(decomp_emld, id.vars="Year")

emld$Group <- ifelse((emld$variable == "emld") | (emld$variable == "eumld"), "Overall",
                     ifelse((emld$variable == "ewithin") | (emld$variable == "euwithin"), "Within group", "Between group"))


emld$Weight <- ifelse((emld$variable == "emld") | (emld$variable == "ewithin") | 
                          (emld$variable == "ebetween"), "Population weighted", "Unweighted")
emld$Group <- factor(emld$Group, levels=c("Overall","Within group", "Between group"))
emld$Weight <- factor(emld$Weight, levels=c("Population weighted","Unweighted"))
```

#### Plot by Energy Expenditure
```{r fig.height = 3, fig.width = 7, fig.align = "center"}
exmld <-ggplot(emld, aes(x=Year))+
  geom_line(aes(y = value, color = Group, linetype = Weight), size=0.7) +
  scale_colour_manual(values=c("black", "green","blue")) +  
  scale_linetype_manual(values=c("solid","dotted")) +
  labs(x = "High-low energy expenditure", y = "")+
  theme(text=element_text(size=8))+
  scale_x_continuous(breaks=c(1997, 2000, 2003, 2006, 2009, 2012, 2015, 2019, 2021)) +
  scale_y_continuous(limits = c(0, 0.22), breaks = seq(0, 0.22, 0.02)) +
  theme(axis.text.x = element_text(angle = 45, vjust=0.5))+
  theme(axis.text.y = element_blank())+
  theme(legend.title = element_blank())+
  theme(legend.direction = "horizontal") +
  theme(legend.position = "none", legend.margin = margin(t = -5)) +
  theme(legend.box = "vertical")+
  theme(legend.background = element_rect(fill = "transparent")) +
  theme(legend.spacing.x = unit(0.3, "lines"))+
  theme(legend.spacing.y = unit(0.6, "lines"))+
  theme(legend.key.width = unit(0.6, 'cm'))+
  theme(legend.key.height = unit(0.5, 'cm'))+
  theme(legend.text = element_text(size=6))
```

#### Plots by Party expenditure and LCV
```{r fig.height = 3, fig.width = 7, fig.align = "center"}

mld_party_ex_lcv <- ggarrange(pmld, exmld, lmld, labels = c("a", "b", "c"), hjust = -2.0, 
                                font.label = list(size = 8, color = "black", face = "bold"), 
                                ncol = 3, nrow = 1, legend="none")
mld_party_ex_lcv
```


#### Decomposition of MLD by income class
```{r}
## Weighted
mld_c <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <- by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- mld_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$in_class, weights = ha[[i]]$pop_mi )
    hb[[i]] <- bar["mld_decomp"]
  }
  return(hb)
}
mld_decomp <- mld_c(dat_p)

### Parse Hash fuction
mldco_decomp <- as.list(mld_decomp)
ml <- lapply(mldco_decomp, function(x) x[1]$mld_decomp)
mldco_decomp <- do.call(rbind.data.frame, ml)
mldco_decomp <- cbind(Year=as.numeric(rownames(mldco_decomp)), mldco_decomp)
rownames(mldco_decomp) <- NULL
mldco_d <- mldco_decomp[order(mldco_decomp$Year, decreasing = FALSE),]
mldco_d <- mldco_d %>% rename(wmld=mld_total, wwithin=mld_within, wbetween=mld_between)

## Unweighted
umld_c <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- mld_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$in_class)
    hb[[i]] <- bar["mld_decomp"]
  }
  return(hb)
}
umld_decomp <- umld_c(dat_p)

### Parse Hash fuction
umldco_decomp <- as.list(umld_decomp)
ml <- lapply(umldco_decomp, function(x) x[1]$mld_decomp)
umldco_decomp <- do.call(rbind.data.frame, ml)
umld_decomp <- cbind(Year=as.numeric(rownames(umldco_decomp)), umldco_decomp)
rownames(umld_decomp) <- NULL
umldco_d <- umld_decomp[order(umld_decomp$Year, decreasing = FALSE),]
umldco_d <- umldco_d %>% rename(umld=mld_total, uwithin=mld_within, ubetween=mld_between)
```

#### Decomposition of MLD by Income
```{r}
## Join files
decomp_mld <- left_join(mldco_d, umldco_d)

## Data preparation
dmld <- reshape2::melt(decomp_mld, id.vars="Year")
dmld$Group <- ifelse((dmld$variable == "wmld") | (dmld$variable == "umld"), "Overall",
                     ifelse((dmld$variable == "wwithin") | (dmld$variable == "uwithin"), "Within group",
                            "Between group"))


dmld$Weight <- ifelse((dmld$variable == "wmld") | (dmld$variable == "wwithin") | 
                          (dmld$variable == "wbetween"), "Population weighted", "Unweighted")

dmld$Group <- factor(dmld$Group, levels=c("Overall","Within group", "Between group"))
dmld$Weight <- factor(dmld$Weight, levels=c("Population weighted","Unweighted"))

## Plot
inmld <-ggplot(dmld, aes(x=Year))+
  geom_line(aes(y = value, color = Group, linetype = Weight), size=0.7) +
  scale_colour_manual(values=c("black", "green","blue")) +  
  scale_linetype_manual(values=c("solid","dotted")) +
  labs(x = "Rich and poor states", y = "")+
  theme(text=element_text(size=8))+
  scale_x_continuous(breaks=c(1997, 2000, 2003, 2006, 2009, 2012, 2015, 2019, 2021)) +
  scale_y_continuous(limits = c(0, 0.22), breaks = seq(0, 0.22, 0.02)) +
  theme(axis.text.x = element_text(angle = 45, vjust=0.5))+
  theme(legend.title = element_blank())+
  theme(legend.direction = "horizontal") +
  theme(legend.position = "bottom", legend.margin = margin(t = -5)) +
  theme(legend.box = "vertical")+
  theme(legend.background = element_rect(fill = "transparent")) +
  theme(legend.spacing.x = unit(0.3, "lines"))+
  theme(legend.spacing.y = unit(0.6, "lines"))+
  theme(legend.key.width = unit(0.6, 'cm'))+
  theme(legend.key.height = unit(0.5, 'cm'))+
  theme(legend.text = element_text(size=6))
```

#### Decomposition by Geography
```{r}
## Weighted
wtgeo_m <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- mld_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$Geography, weights = ha[[i]]$pop_mi)
    hb[[i]] <- bar["mld_decomp"]
  }
  return(hb)
}
wtgeomld <- wtgeo_m(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_wtgeom <- as.list(wtgeomld)
wgeom <- lapply(list_wtgeom, function(x) x[1]$mld_decomp)
df_wtgeom <- do.call(rbind.data.frame, wgeom)
df_wtgeom <- cbind(Year=as.numeric(rownames(df_wtgeom)), df_wtgeom)
rownames(df_wtgeom) <- NULL
df_wtgeom <- df_wtgeom[order(df_wtgeom$Year, decreasing = FALSE),]
wtg_geom <- df_wtgeom %>% rename(wtotal=mld_total, wwithin=mld_within, wbetween=mld_between)

## unweighted
ungeom <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- mld_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$Geography)
    hb[[i]] <- bar["mld_decomp"]
  }
  return(hb)
}
ungeodm <- ungeom(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_ungeom <- as.list(ungeodm)
ugm <- lapply(list_ungeom, function(x) x[1]$mld_decomp)
df_ungeom <- do.call(rbind.data.frame, ugm)
df_ungeom <- cbind(Year=as.numeric(rownames(df_ungeom)), df_ungeom)
rownames(df_ungeom) <- NULL
df_ungeom <- df_ungeom[order(df_ungeom$Year, decreasing = FALSE),]
ug_geom <- df_ungeom %>% rename(total=mld_total, 
                                 within=mld_within, between=mld_between)

```
</br>

#### Data preparation: Geography
```{r}
## Join files
decomp_geom <-left_join(ug_geom, wtg_geom)

## Data preparation
dgeom <- reshape2::melt(decomp_geom, id.vars="Year")
dgeom$Group <- ifelse((dgeom$variable == "wtotal") | (dgeom$variable == "total"), "Overall",
                       ifelse((dgeom$variable == "wwithin") | (dgeom$variable == "within"), "Within group","Between group"))


dgeom$Weight <- ifelse((dgeom$variable == "wtotal") | (dgeom$variable == "wwithin") | 
                          (dgeom$variable == "wbetween"), "Population Weighted", "Unweighted")

dgeom$Group <- factor(dgeom$Group, levels=c("Overall","Within group", "Between group"))
dgeom$Weight <- factor(dgeom$Weight, levels=c("Population Weighted","Unweighted"))
```

#### Decompostion plot: Geography
```{r fig.height = 3, fig.width = 3, fig.align = "center"}
mldgeom <-ggplot(dgeom, aes(x=Year))+
  geom_line(aes(y = value, color = Group, linetype = Weight), size=0.7) +
  scale_colour_manual(values=c("black", "green","blue")) +  
  scale_linetype_manual(values=c("solid","dotted")) +
  labs(x = "Coastal-non-coastal states", y = "")+
  theme(text=element_text(size=8))+
  scale_y_continuous(limits = c(0, 0.22), breaks = seq(0, 0.22, 0.02)) +
  scale_x_continuous(breaks=c(1997, 2000, 2003, 2006, 2009, 2012, 2015, 2019, 2021)) +
  theme(axis.text.x = element_text(angle = 45, vjust=0.5))+
  theme(axis.text.y = element_blank())+
  theme(legend.title = element_blank())+
  theme(legend.direction = "horizontal") +
  theme(legend.position = "bottom", legend.margin=margin(t = 1)) +
  theme(legend.box = "vertical")+
  theme(legend.background = element_rect(fill = "transparent")) +
  theme(legend.spacing.x = unit(0.2, "lines"))+
  theme(legend.spacing.y = unit(0.6, "lines"))+
  guides(linetype = guide_legend(order = 1),col = guide_legend(order = 2))+
  theme(legend.key.width = unit(0.35, 'cm'))+
  theme(legend.key.height = unit(0.4, 'cm'))+
  theme(legend.text = element_text(size=6))+
  scale_color_manual(labels = c("Overall", "Within group", "Between group"), values=c("black", "green","blue"))
```

#### Decomposition by Heating Degree Days
```{r}
## Weighted
wthddm <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- mld_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$HDD, weights = ha[[i]]$pop_mi)
    hb[[i]] <- bar["mld_decomp"]
  }
  return(hb)
}
wth_days <- wthddm(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_wtheat <- as.list(wth_days)
wheat <- lapply(list_wtheat, function(x) x[1]$mld_decomp)
df_wtheat <- do.call(rbind.data.frame, wheat)
df_wtheat <- cbind(Year=as.numeric(rownames(df_wtheat)), df_wtheat)
rownames(df_wtheat) <- NULL
df_wtheat <- df_wtheat[order(df_wtheat$Year, decreasing = FALSE),]
wtg_heatm <- df_wtheat %>% rename(wtotal=mld_total, wwithin=mld_within, wbetween=mld_between)

## unweighted
unheatm <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- mld_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$HDD)
    hb[[i]] <- bar["mld_decomp"]
  }
  return(hb)
}
unh_days <- unheatm(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_unheat <- as.list(unh_days)
unheat <- lapply(list_unheat, function(x) x[1]$mld_decomp)
df_unheat <- do.call(rbind.data.frame, unheat)
df_unheat <- cbind(Year=as.numeric(rownames(df_unheat)), df_unheat)
rownames(df_unheat) <- NULL
df_unheat <- df_unheat[order(df_unheat$Year, decreasing = FALSE),]
un_heatm <- df_unheat %>% rename(untotal=mld_total, unwithin=mld_within, unbetween=mld_between)

```


#### Data preparation: HDD
```{r}
## Join files
decomp_mhdd <-left_join(wtg_heatm, un_heatm)

## Data preparation
dheat <- reshape2::melt(decomp_mhdd, id.vars="Year")
dheat$Group <- ifelse((dheat$variable == "wtotal") | (dheat$variable == "untotal"), "Overall",
                       ifelse((dheat$variable == "wwithin") | (dheat$variable == "unwithin"), "Within group", "Between group"))


dheat$Weight <- ifelse((dheat$variable == "wtotal") | (dheat$variable == "wwithin") | 
                          (dheat$variable == "wbetween"), "Population Weighted", "Unweighted")

dheat$Group <- factor(dheat$Group, levels=c("Overall","Within group", "Between group"))
dheat$Weight <- factor(dheat$Weight, levels=c("Population Weighted","Unweighted"))
```

#### Decompostion plot: HDD
```{r fig.height = 3, fig.width = 3, fig.align = "center"}

mldheat<-ggplot(dheat, aes(x=Year))+
  geom_line(aes(y = value, color = Group, linetype = Weight), size=0.7) +
  scale_linetype_manual(values=c("solid","dotted")) +
  labs(x = "High-low heating degree days", y = "")+
  theme(text=element_text(size=8))+
  scale_y_continuous(limits = c(0, 0.22), breaks = seq(0, 0.22, 0.02)) +
  scale_x_continuous(breaks=c(1997, 2000, 2003, 2006, 2009, 2012, 2015, 2019, 2021)) +
  theme(axis.text.x = element_text(angle = 45, vjust=0.5))+
  theme(axis.text.y = element_blank())+
  theme(legend.title = element_blank())+
  theme(legend.direction = "horizontal") +
  theme(legend.position = "bottom", legend.margin=margin(t= 1)) +
  theme(legend.box = "vertical")+
  theme(legend.background = element_rect(fill = "transparent")) +
  theme(legend.spacing.x = unit(0.3, "lines"))+
  theme(legend.spacing.y = unit(0.6, "lines"))+
  theme(legend.key.width = unit(0.35, 'cm'))+
  theme(legend.key.height = unit(0.4, 'cm'))+
  theme(legend.text = element_text(size=7))+
  scale_color_manual(labels = c("Overall", "Within group", "Between group"), values=c("black", "green","blue"))
```

#### Decomposition by Cooling Degree Days
```{r}
## Weighted
wtcddm <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- mld_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$CDD, weights = ha[[i]]$pop_mi)
    hb[[i]] <- bar["mld_decomp"]
  }
  return(hb)
}
wtc_days <- wtcddm(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_wtcool <- as.list(wtc_days)
wcool <- lapply(list_wtcool, function(x) x[1]$mld_decomp)
df_wtcool <- do.call(rbind.data.frame, wcool)
df_wtcool <- cbind(Year=as.numeric(rownames(df_wtcool)), df_wtcool)
rownames(df_wtcool) <- NULL
df_wtcool <- df_wtcool[order(df_wtcool$Year, decreasing = FALSE),]
wtg_coolm <- df_wtcool %>% rename(wtotal=mld_total, wwithin=mld_within, wbetween=mld_between)

## unweighted
uncoolm <- function(dat_p){
  ha <-hash()
  for(j in 1997:2021){
    ha[[as.character(j)]] <-by_year(dat_p, j)
  } 
  hb <- hash()
  keys_ha <- keys(ha)
  for(i in keys_ha) {
    bar <- mld_decomp(x=ha[[i]]$pc_CO2, z=ha[[i]]$CDD)
    hb[[i]] <- bar["mld_decomp"]
  }
  return(hb)
}
unc_days <- uncoolm(dat_p)

### PARSE HASH FUNCTION OUTPUT ---
list_uncool <- as.list(unc_days)
uncool <- lapply(list_uncool, function(x) x[1]$mld_decomp)
df_uncool <- do.call(rbind.data.frame, uncool)
df_uncool <- cbind(Year=as.numeric(rownames(df_uncool)), df_uncool)
rownames(df_uncool) <- NULL
df_uncool <- df_uncool[order(df_uncool$Year, decreasing = FALSE),]
un_coolm <- df_uncool %>% rename(untotal=mld_total, unwithin=mld_within, unbetween=mld_between)
```

#### Data preparation: CDD
```{r}
## Join files
decomp_cddm <-left_join(wtg_coolm, un_coolm)

## Data preparation
dcool <- reshape2::melt(decomp_cddm, id.vars="Year")
dcool$Group <- ifelse((dcool$variable == "wtotal") | (dcool$variable == "untotal"), "Overall",
                       ifelse((dcool$variable == "wwithin") | (dcool$variable == "unwithin"), "Within group","Between group"))


dcool$Weight <- ifelse((dcool$variable == "wtotal") | (dcool$variable == "wwithin") | 
                          (dcool$variable == "wbetween"), "Population Weighted", "Unweighted")

dcool$Group <- factor(dcool$Group, levels=c("Overall","Within group", "Between group"))
dcool$Weight <- factor(dcool$Weight, levels=c("Population Weighted","Unweighted"))
```

#### Decompostion plot: CDD
```{r fig.height = 3, fig.width = 3, fig.align = "center"}

mldcool<-ggplot(dcool, aes(x=Year))+
  geom_line(aes(y = value, color = Group, linetype = Weight), size=0.7) +
  #scale_colour_manual(values=c("black", "green","blue", "red")) +  
  scale_linetype_manual(values=c("solid","dotted")) +
  labs(x = "High-low cooling degree days", y = "")+
  theme(text=element_text(size=8))+
  scale_y_continuous(limits = c(0, 0.22), breaks = seq(0, 0.22, 0.02)) +
  scale_x_continuous(breaks=c(1997, 2000, 2003, 2006, 2009, 2012, 2015, 2019, 2021)) +
  theme(axis.text.x = element_text(angle = 45, vjust=0.5))+
  theme(axis.text.y = element_blank())+
  theme(legend.title = element_blank())+
  theme(legend.direction = "horizontal") +
  theme(legend.position = "bottom", legend.margin=margin(t= 1)) +
  theme(legend.box = "vertical")+
  theme(legend.background = element_rect(fill = "transparent")) +
  theme(legend.spacing.x = unit(0.3, "lines"))+
  theme(legend.spacing.y = unit(0.6, "lines"))+
  theme(legend.key.width = unit(0.35, 'cm'))+
  theme(legend.key.height = unit(0.4, 'cm'))+
  theme(legend.text = element_text(size=7))+
  scale_color_manual(labels = c("Overall", "Within group", "Between group"), values=c("black", "green","blue"))
```

#### Decomposition Plot by Income, Geography and Heating/Cooling Degree Days
```{r fig.height = 3, fig.width = 7, fig.align = "center"}

mld_in_geo_days <-ggarrange(inmld, mldgeom, mldheat, mldcool, labels = c("d", "e", "f", "g"), hjust = -2.0, 
                                font.label = list(size = 8, color = "black", face = "bold"), 
                                ncol = 4, nrow = 1, common.legend = TRUE, legend ="bottom")
mld_in_geo_days
```

#### All MLD Decomposition Plots
```{r fig.height = 6, fig.width = 7, fig.align = "center"}

decomp_MLD <- ggarrange(mld_party_ex_lcv, mld_in_geo_days, nrow=2)
decomp_MLD <- annotate_figure(decomp_MLD, left = text_grob("Decomposition of per capita CO2 Gini", rot=90, size=8))

decomp_MLD

## plot file output
file.plot <- file.path(dir.plot, "mld_decomp.png")
png(file.plot, height=6, width=7, units="in", bg= "white", res=300)
decomp_MLD
dev.off()
```